Model diagnostics

### 2023-09-15 notebook/analysis-issue.qmd
Better handling of outcome labels

```{r plot-pred-discrete-continuous-local-bars, fig.width=8, fig.height=3, out.width="100%"}
preds_issue_plot <- preds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces"
  )) |> 
  mutate(outcome = factor(
    outcome, 
    levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"))
  ) |> 
  group_by(outcome, issue_area_nice, draw) |> 
  summarize(count = n()) |> 
  group_by(issue_area_nice, draw) |> 
  mutate(prop = count / sum(count))

>>>>

```{r plot-pred-discrete-continuous-local-bars, fig.width=8, fig.height=3, out.width="100%"}
preds_issue_plot <- preds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  group_by(outcome, issue_area_nice, draw) |> 
  summarize(count = n()) |> 
  group_by(issue_area_nice, draw) |> 
  mutate(prop = count / sum(count))

### 2023-09-15 notebook/analysis-timing.qmd
Better handling of outcome labels

```{r plot-pred-discrete-continuous-timing-area}
preds_timing_plot <- preds_timing |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  mutate(years_since_law = 2017 + years_since_law) |> 
  group_by(outcome, years_since_law, draw) |>
  summarize(count = n()) |> 
  group_by(years_since_law) |> 
  mutate(prop = count / sum(count) * 100)

>>>>

```{r plot-pred-discrete-continuous-timing-area}
preds_timing_plot <- preds_timing |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  mutate(years_since_law = 2017 + years_since_law) |> 
  group_by(outcome, years_since_law, draw) |>
  summarize(count = n()) |> 
  group_by(years_since_law) |> 
  mutate(prop = count / sum(count) * 100)

### 2023-09-15 notebook/model-diagnostics.qmd
Use coefficient that actually exists
Add ordered beta illustration + model results table
Better handling of outcome labels

```{r}
get_variables(m_full_ordbeta)
```

### Traceplots

@@

```{r mcmc-trace}
params_to_show <- c(
  "b_Intercept", "b_work_field_code1Health",
  "phi", "cutzero"
)

@@

### Trace rank plots (trank plots)

@@

## Posterior predictions

@@

posterior_categories <- full_posterior |> 
  ungroup() |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1",
    .prediction > 0 & .prediction < 1 ~ "1–32",
    .prediction == 1 ~ "32"
  )) |> 
  group_by(outcome, .draw) |> 
  summarize(count = n()) |> 
  ungroup()

actual_counts <- m_full_ordbeta$data |> 
  mutate(outcome = case_when(
    province_count == 0 ~ "1",
    province_count > 0 & province_count < 1 ~ "1–32",
    province_count == 1 ~ "32"
  )) |> 
  group_by(outcome) |> 
  summarize(count = n())

>>>>

# Traceplots

@@

```{r mcmc-trace}
params_to_show <- c(
  "b_Intercept", "b_issue_healthTRUE",
  "phi", "cutzero"
)

@@

# Trace rank plots (trank plots)

@@

# Posterior predictions

@@

posterior_categories <- full_posterior |> 
  ungroup() |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  group_by(outcome, .draw) |> 
  summarize(count = n()) |> 
  ungroup()

actual_counts <- m_full_ordbeta$data |> 
  mutate(outcome = case_when(
    province_count == 0 ~ "Only 1 province",
    province_count > 0 & province_count < 1 ~ "Between 1–32 provinces",
    province_count == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  group_by(outcome) |> 
  summarize(count = n())
